Object naming is context dependent - A case study on testing linguistic hypotheses on real-world image corpora

### 2018-07-12 papers/SiVL2018/sivl_2018.tex
intermediate commit

\newcommand{\refexp}[1]{\textsl{#1}}
\newcommand{\cat}[1]{\textsc{#1}}

@@

Despite this dramatic progress in the field, however, a lot of research in language \& vision still centers around systems for very specific tasks and data sets.

>>>>

\newcommand{\refexp}[1]{\textsl{#1}}
\newcommand{\word}[1]{\textsl{#1}}
\newcommand{\cat}[1]{\textsc{#1}}

\newcommand{\green}[1]{\textcolor{PineGreen}{#1}}
\newcommand{\red}[1]{\textcolor{red}{#1}}
\newcommand{\blue}[1]{\textcolor{blue}{#1}}
\newcommand{\yellow}[1]{\textcolor{yellow}{#1}}

@@

Despite this dramatic progress in the field, however, a lot of research in language \& vision still centers around systems and applications for very specific tasks and data sets.
Most of the influential papers have investigated which modeling architectures need to be adopted to re-generate human descriptions or utterances in a particular data set, whereas studies aimed at obtaining linguistic generalizations from existing data collections and models are relatively rare.
